Nirdizati: A Web-based Tool for Predictive Process Monitoring

### 2017-06-16 BPM17-demo-paper/paper.tex
abstracts merged

\begin{abstract}
%In this paper, we present a prototype of a predictive process monitoring engine for process workers and operational managers.
%The developed solution, named \emph{Nirdizati}, is a configurable full-stack web application that supports users in selecting the preferred prediction method from the list of implemented methods and enables the continuous prediction of various performance indicators at runtime.
%The results of the predictions, as well as the real-time summary statistics about the process execution, are presented in a dashboard that offers multiple visualization options.
%The target audience of this demonstration includes process mining researchers as well as practitioners interested in exploring the potential of process monitoring.
%In this paper, we present Nirdizati, an open-source tool for predictive monitoring of business processes.
%The tool can be used to predict the outcome, the next events, or the remaining time of each case of a process.
%For example, in an lead-to-order process, Nirdizati can predict which customer leads will convert to purchase orders and when.
%In a claims handling process, Nirdizati can predict if a claim decision will be made on time or late.
%Based on these predictions, process workers and operational managers can act proactively to resolve or mitigate potential process performance violations.
%The target audience of this demonstration includes process mining researchers as well as practitioners interested in exploring the potential of process monitoring.
In this paper, we present a prototype of a web-based application for predictive process monitoring that can be used by process workers and operational managers to predict the future development of a currently running process execution.
The implemented solution, named \emph{Nirdizati}, is a configurable full-stack web application that supports users in selecting the preferred prediction methods from a list of implemented algorithms and enables the continuous prediction of various measures of interest at runtime. The results of the predictions, as well as the real-time summary statistics about the process executions, are presented in a dashboard that offers multiple visualization options. The target audience of this demonstration includes process mining researchers as well as practitioners interested in exploring the potential of predictive process monitoring.

>>>>

\begin{abstract}
%In this paper, we present a prototype of a predictive process monitoring engine for process workers and operational managers.
%The developed solution, named \emph{Nirdizati}, is a configurable full-stack web application that supports users in selecting the preferred prediction method from the list of implemented methods and enables the continuous prediction of various performance indicators at runtime.
%The results of the predictions, as well as the real-time summary statistics about the process execution, are presented in a dashboard that offers multiple visualization options.
%The target audience of this demonstration includes process mining researchers as well as practitioners interested in exploring the potential of process monitoring.
In this paper, we present Nirdizati, a web-based application for predictive process monitoring that can be used to predict the future development of a currently running process execution. The implemented solution is a configurable full-stack web application that supports users in selecting the preferred prediction methods from a list of implemented algorithms and enables the continuous prediction of various measures of interest at runtime.
The tool can be used to predict the outcome, the next events, or the remaining time of each case of a process.
For example, in an lead-to-order process, Nirdizati can predict which customer leads will convert to purchase orders and when.
In a claims handling process, Nirdizati can predict if a claim decision will be made on time or late.
%Based on these predictions, process workers and operational managers can act proactively to resolve or mitigate potential process performance violations.
%The target audience of this demonstration includes process mining researchers as well as practitioners interested in exploring the potential of process monitoring.
%In this paper, we present a prototype of a web-based application for predictive process monitoring that can be used by process participants and operational managers to predict the future development of a currently running process execution.
%The implemented solution, named \emph{Nirdizati}, is a configurable full-stack web application that supports users in selecting the preferred prediction methods from a list of implemented algorithms and enables the continuous prediction of various measures of interest at runtime. 
The results of the predictions, as well as the real-time summary statistics about the process executions, are presented in a dashboard that offers multiple visualization options. The target audience of this demonstration includes process mining researchers as well as practitioners interested in exploring the potential of predictive process monitoring. Based on these predictions, process participants can act proactively to resolve or mitigate potential process performance violations.
